Dark matter halo shape in the Auriga simulations: radial dependence, time evolution and correlation with baryon disk properties

### 2019-07-17 Document/paper.tex
caption last figure

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{correlation_T_MHD_disk.pdf}
\end{center}
\caption{Correlations between the halo triaxility at different radii
  and baryonic disk properties. 
  The label with the $\rho$ value corresponds to the Spearman's rank
  correlation coefficient.
  The line is the best linear minimum squares fit.
  The x-axis in the first column is the gas density at the center of
  the galaxy with in a sphere of radius  $1$ kpc \citep{Pakmor17};
  the second column shows the disk to total mass ratio and the last
  column includes the disk optical radius defined to be the radius at which the
  $B$-band surface brightness drops below 25 mag arcsec$^-2$
  \citep{auriga}.
  The largest correlations are found for the two smaller radii and
  dilute as one approached $R_{200}$.
  Large and massive stellar disks with a low gas content are
  correlated with low dark matter triaxilities.
}
\label{fig:disk_correlations}
\end{figure*}

\begin{figure}
\begin{center}
\includegraphics[width=0.45\textwidth]{triaxiality_observations.pdf}
\end{center}
\caption{A}
\label{fig:observations}
\end{figure}

@@

%\begin{figure*}
%  \centering
%  \subfloat[Perfectly aligned Axes]{\includegraphics[width=0.6\columnwidth]{./pics/well_axes.png}}
%  \hfill
%  \subfloat[Somewhat aligned Axes]{\includegraphics[width=0.6\columnwidth]{./pics/rotating_axes.png}}
%  \hfill
%  \subfloat[Chaotic Axes]{\includegraphics[width=0.6\columnwidth]{./pics/chaotic_axes.png}}
%  \hfill
%  \caption{Star: Minor Axis
%    Triangle: Medium Axis
%    Square: Major Axis
%    Color: Radii at which shape was sampled (show radii sampled)
%    Contour color: If orientation is above or below in this projection
%    Cross (black): Orientation of the stellar disk
%    Conclusion: Axes (minor) are not (generally) aligned with the
%    stellar disk nor are they usually aligned with each other from
%    different radii. We show some cases that may happen.} 
%  \label{fig:alignment}
%\end{figure*}

\textbf{Discussion about the distribution of alignments and their
  evolution in time: Precesion or temporary instabilities?}

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{correlation_T_MHD_disk.pdf}
\end{center}
\caption{Correlations between the halo triaxility at different radii
  and baryonic disk properties. 
  The label with the $\rho$ value corresponds to the Spearman's rank
  correlation coefficient.
  The line is the best linear minimum squares fit.
  The x-axis in the first column is the gas density at the center of
  the galaxy with in a sphere of radius  $1$ kpc \citep{Pakmor17};
  the second column shows the disk to total mass ratio and the last
  column includes the disk optical radius defined to be the radius at which the
  $B$-band surface brightness drops below 25 mag arcsec$^-2$ \citep{auriga}.
  The largest correlations are found for the two smaller radii and
  dilute as one approached $R_{200}$.
  Large and massive stellar disks with a low gas content are
  correlated with low dark matter triaxilities.}
\label{fig:disk_correlations}
\end{figure*}

\begin{figure}
\begin{center}
\includegraphics[width=0.45\textwidth]{triaxiality_observations.pdf}
\end{center}
\caption{Comparison of our results against other simulations
  by \citet{Chua19} (Illustris) and observational constraints for the 
dark matter halo shape in the Milky Way by \citet{LM10} (LM10) and
\citet{Bovy16} (BBFK16).   
We report our results in the MHD simulations in such a way as to
bracket the radii in the other estimates.
We find that our results are broadly consistent with the Illustris
simulations given the broad dispersion in both data sets.
The consistency with the constraints by \citet{Bovy16} is marginal,
only 1/5 of the halos in our sample seem to be consistent within the
observational reults.
The result by \citet{LM10} would place the Milky Way halo as an
atypical object in the $\Lambda$ CDM context.} 
\label{fig:observations}
\end{figure}

@@
